How many times must an object be named (before we know what it is)?

### 2019-01-03 papers/ACL2019/acl19_naming.tex
adds a few comments

\documentclass[11pt]{article}
%\usepackage[hyperref]{acl2017}
\usepackage[nohyperref]{acl2017}
\usepackage{times}
\usepackage{url}
\usepackage{latexsym}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{graphicx}  %%% for including graphics
\usepackage{rotating}
\usepackage{color}

@@

\newcommand{\sz}[1]{\textcolor{blue}{\emph{//sz: #1//}}}
\newcommand{\das}[1]{\textcolor{red}{\emph{//das: #1//}}}
\newcommand{\refexp}[1]{\textsl{#1}}
\newcommand{\word}[1]{\textsl{#1}}
\newcommand{\cat}[1]{\textsc{#1}}
\newcommand{\vgenome}{VisualGenome\xspace}

@@

In NLP, to date, research on object naming is relatively scarce despite the fact that
 there has been a recent explosion of interest in various, and even complex, language \& vision tasks ranging from image captioning \cite{fangetal:2015,devlin:imcaqui,Bernardietal:automatic} to e.g.\ visual dialogue \cite{das2017visual,vries2017guesswhat}. Massive data collections for applications in language \& vision (L\&V) are nowadays available and, in principle, these should also constitute an excellent, large-scale test beds for assessing  theories such as, e.g.\ , the claim that objects have a preferred entry-level when being named  \cite{rosch1976basic}.
%In this paper, we argue that a lot of research in this area would benefit from a deeper and more systematic understanding of the semantic and taxonomic processes in object naming, which is a core phenomenon in virtually every vision \& language task.
%At the same time, we argue that existing resources in L\&V constitute an excellent, large-scale test bed for assessing traditional claims and theories such as, e.g.\ the existence of so-called entry-level categories  \cite{rosch1976basic}.

@@

Even though VisualGenome is one of the most exhaustively annotated resources to date, providing dense object annotations and descriptions in real-world images, it suffers from two important shortcomings if one is interested in linguistic analysis of object naming:  
First, it only provides a single, manually annotated object description (including a single name) per object which makes it impossible to assess how representative the annotated naming choices are, e.g.\ whether speakers tend to generally prefer \refexp{cheesecake} for the highlighted object in Figure \ref{fig:cake}.
Second, it does not provide consistent taxonomic information on objects and their categories, as names have been automatically linked to WordNet synsets. 
This makes it difficult to assess how naming depends on the taxonomic properties of the object, e.g.\  that both objects in Figure \ref{fig:cake} are instances of \cat{cheesecake}, but one is named \refexp{cheesecake} and the other one is named \refexp{desert}. It is important to note here that this shortcomings exist for basically all large-scale resources currently used in L \&V research (see Section 2 below).

@@

The main idea is to elicit names in (i) in a standard naming task (phase 0) where participants simply give the most straightforward name to an object they can immediately think of, and then in (ii) a taboo-like naming task where frequent names collected initially are blocked and participants have to provide alternative names. We show that this cheap, two-stage approach gives us taxonomically rich data that allows us to study object naming empirically, without adopting costly annotation procedures involving complex hierarchical object annotation schemes.

@@

 Seminal work on concepts by Rosch suggests that object names typically exhibit a preferred level of specificity called the \textbf{entry-level}. This typically corresponds to an intermediate level of specificity, i.e., \textbf{basic level} (e.g, \refexp{bird}, \refexp{car}) \cite{rosch1976basic}, as opposed to more generic (i.e., \textbf{super-level}; e.g., \refexp{animal}, \refexp{vehicle}) or specific categories (i.e., \textbf{sub-level}; e.g., \refexp{sparrow}, \refexp{convertible}). However, less prototypical members of basic-level categories tend to be instead identified with sub-level categories (e.g., a \cat{penguin} is typically called a \refexp{penguin} and not a \refexp{bird}) \cite{jolicoeur1984pictures}. 
%This out-of-context preference towards a certain taxonomic level is often referred to as \textbf{lexical availability}. 
While the traditional notion of entry-level categories suggests that objects tend to be named by a \refexp{single} preferred concept, research on pragmatics has found that speakers are flexible in  
%with respect to the chose level of specificity. 
their choice of the level of specificity. 
Scenarios where multiple objects (of the same category) are present induce a pressure for generating names which uniquely identify the target \cite{olson1970language}, such that sub-level names can be systematically elicited in these cases %\cite{rohde2012communicating} \cite{graf2016animal}. 
\cite{rohde2012communicating}\cite{graf2016animal}.

@@

State-of-the-art computer vision systems are able to classify images into thousands of different categories (e.g.\  \newcite{googlenet}). These object recognition systems are now widely used in vision \& language research.
Nevertheless, the way the treat object recognition is conceptually very simple (if not to say, naive):  standard object classification schemes are inherently ``flat'', and treat object labels as mutually exclusive \cite{deng2014large}, ignoring all kinds of linguistic relations between these labels and ignoring the fact that an object can easily be an instance of several categories.

@@

\paragraph{Existing resources and their shortcomings}
Moreover, existing resources in L\&V hardly provide any consistent taxonomic information on objects and their categories, e.g. object labels are typically quite general as in Flickr30k \cite{plummer2015flickr30kentities} (e.g.,~\cat{people, animals, bodyparts, clothing}) or taxonomically heterogeneous as in MS COCO \cite{mscoco} (e.g.,~\cat{people, baseball glove, bird}).

@@

\begin{itemize}
\item  analyse naming disagreement using WordNet, how do names for the same object relate to each other according to WordNet?
\item can we identify instances of cross-classification? so objects that are systematically part of several classes (e.g. cake/dessert)
\item we might need to do some manual annotation here and try to carefully describe the phenomena
\end{itemize}

>>>>

\documentclass[11pt]{article}
%\usepackage[hyperref]{acl2017}
\usepackage[nohyperref]{acl2017}
\usepackage{times}
\usepackage{url}
\usepackage{latexsym}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{graphicx}  %%% for including graphics
\usepackage{rotating}
\usepackage[dvipsnames]{xcolor}

@@

\newcommand{\sz}[1]{\textcolor{blue}{\emph{//sz: #1//}}}
\newcommand{\cs}[1]{\textcolor{Fuchsia}{\emph{//cs: #1//}}}
\newcommand{\refexp}[1]{\textsl{#1}}
\newcommand{\word}[1]{\textsl{#1}}
\newcommand{\cat}[1]{\textsc{#1}}
\newcommand{\vgenome}{VisualGenome\xspace}

@@

In NLP, to date, research on object naming is relatively scarce despite the fact that
 there has been a recent explosion of interest in various, and even complex, language \& vision tasks ranging from image captioning \cite{fangetal:2015,devlin:imcaqui,Bernardietal:automatic} to e.g.\ visual dialogue \cite{das2017visual,vries2017guesswhat}. Massive data collections for applications in language \& vision (L\&V) are nowadays available and, in principle, these should also constitute an excellent, large-scale test bed for assessing  theories such as, e.g.\ , the claim that objects have a preferred entry-level when being named  \cite{rosch1976basic}.
%In this paper, we argue that a lot of research in this area would benefit from a deeper and more systematic understanding of the semantic and taxonomic processes in object naming, which is a core phenomenon in virtually every vision \& language task.
%At the same time, we argue that existing resources in L\&V constitute an excellent, large-scale test bed for assessing traditional claims and theories such as, e.g.\ the existence of so-called entry-level categories  \cite{rosch1976basic}.

@@

Even though VisualGenome is one of the most exhaustively annotated resources to date, providing dense object annotations and descriptions in real-world images, it suffers from two important shortcomings if one is interested in linguistic analysis of object naming:  
First, it only provides a single, manually annotated object description (including a single name) per object which makes it impossible to assess how representative the annotated naming choices are, e.g.\ whether speakers tend to generally prefer \refexp{cheesecake} for the highlighted object in Figure \ref{fig:cake}.
Second, it does not provide consistent taxonomic information on objects and their categories, as names have been automatically linked to WordNet synsets. 
This makes it difficult to assess how naming depends on the taxonomic properties of the object, e.g.\  that both objects in Figure \ref{fig:cake} are instances of \cat{cheesecake}, but one is named \refexp{cheesecake} and the other one is named \refexp{desert}. It is important to note here that these shortcomings exist for basically all large-scale resources currently used in L \&V research (see Section 2 below).

@@

The main idea is to elicit names in (i) in a standard naming task (phase 0) where participants simply give the most straightforward name to an object they can immediately think of, and then in (ii) a taboo-like naming task where frequent names collected initially are blocked and participants have to provide alternative names. We show that this simple, two-stage approach gives us taxonomically rich data that allows us to study object naming empirically, without adopting costly annotation procedures involving complex hierarchical object annotation schemes.

@@

 Seminal work on concepts by Rosch suggests that object names typically exhibit a preferred level of specificity called the \textbf{entry-level}. This typically corresponds to an intermediate level of specificity, i.e., \textbf{basic level} (e.g, \refexp{bird}, \refexp{car}) \cite{rosch1976basic}, as opposed to more generic (i.e., \textbf{super-level}; e.g., \refexp{animal}, \refexp{vehicle}) or specific categories (i.e., \textbf{sub-level}; e.g., \refexp{sparrow}, \refexp{convertible}). However, less prototypical members of basic-level categories tend to be instead identified with sub-level categories (e.g., a \cat{penguin} is typically called a \refexp{penguin} and not a \refexp{bird}) \cite{jolicoeur1984pictures}. 
%This out-of-context preference towards a certain taxonomic level is often referred to as \textbf{lexical availability}. 
While the traditional notion of entry-level categories suggests that objects tend to be named by a \refexp{single} preferred concept, research on pragmatics has found that speakers are flexible in  
%with respect to the chose level of specificity. 
their choice of the level of specificity. 
Scenarios where multiple objects (of the same category) are present induce a pressure for generating names which uniquely identify the target \cite{olson1970language}, such that sub-level names can be systematically elicited in these cases %\cite{rohde2012communicating} \cite{graf2016animal}. 
\cite{rohde2012communicating,graf2016animal}.

@@

State-of-the-art computer vision systems are able to classify images into thousands of different categories (e.g.\  \newcite{googlenet}). These object recognition systems are now widely used in vision \& language research.
Nevertheless, the way the treat object recognition is conceptually very simple (if not to say, naive):  standard object classification schemes are inherently ``flat'', and treat object labels as mutually exclusive \cite{deng2014large}, ignoring all kinds of linguistic relations between these labels and ignoring the fact that an object can easily be an instance of several categories.\cs{I would make this statement stronger and argue that \textbf{object recognition is merely a labeling of objects  with human interpretable symbols}, and that a system would probably fail if it had to decide whether an object labeled as, e.g.\ \refexp{fig} may also be labeled as \refexp{food}.}

@@

\paragraph{Existing resources and their shortcomings}
Moreover, existing resources in L\&V hardly provide any consistent taxonomic information on objects and their categories, e.g. object labels are typically quite general as in Flickr30k \cite[e.g.,~\cat{people, animals, bodyparts, clothing}]{plummer2015flickr30kentities} or taxonomically heterogeneous as in MS COCO \cite[e.g.,~\cat{people, baseball glove, bird}]{mscoco}.

@@

\begin{itemize}
\item  analyse naming disagreement using WordNet, how do names for the same object relate to each other according to WordNet?
\item can we identify instances of cross-classification? so objects that are systematically part of several classes (e.g. cake/dessert)
\item \cs{Wrt points 1+2: Show that WordNet, again, is not ideal for retrieving all possible names of an object from a single synset.}
\item we might need to do some manual annotation here and try to carefully describe the phenomena
\end{itemize}
